Insert the article title here

### 2020-07-25 tex/results.tex
some polishing on Ellis

 %%% Ellis work summary %%%%
The work of Ellis and coworkers \cite{ellis2016} study the aspect-ratio evolution of high-order
resonant modes in localized surface phonon-polariton nanostructures. They study the
excitation of multipolar localized surface phonon polaritons (SPhP) resonances, by measuring
polarized reflectance measurements on 4H-SiC pillars of fixed height ($H=950$ nm), fixed 
width ($W=400$ nm) and varied length ($L=400-4800$ nm) and therefore an aspect ratio
($AR=L/W=1-12$). These pillars are patterned on a squared grid with a pitch $P=L+500$ nm
to reduce coupling. In their simulations and experiments they excite the localized SPhP
resonances, they perform polarized reflectance measurements with the incident polarization 
oriented parallel or perpendicular to the long axis of the pillars.  
 %%% Ellis work summary %%%%

We aim to replicate the computational result presented in Figure S4 of their supplementary 
material (NOT SURE HOW TO CITE THIS) that correspond to the black curve on their plot. In this 
figure they show simulation results for the resonance spectral position of the lower frequency 
mode when having parallel polarization ($E^{\parallel}_{100}$), with an incidence angle of 22$^\circ$.
We first attempted to replicate this result since they have simulations with the gap between pillars 
is 5000 nm, and this cause negligible coupling. This result is suitable to compare with 
what we can model using \pygbe.

@@

\textit{methods}
In Ellis et al simulations they solve full Maxwell equations via the RF package of the finite
element method software COMSOL. To represent the array of pillars and their interactions, they use
periodic boundary conditions of one pillar over a portion of substrate. They present the reflectance 
as a function of the wave number. As we mentioned before, we use the boundary element method in 
the quasistatic approximation, which is suitable in these case since Ellis pillar's size is small 
compared to the wavelength involved in the simulations (800-1000 cm$^-1$). We measure extinction cross 
section, which will express as peaks instead of inverted peaks (as in reflection) since you see maximum
extinction when there is minimum reflection. The intensity of the peaks is not comparable, but we are 
looking to match the wave number at which these events happen.

\textit{mesh}
For the case of aspect ratio AR=4 we count with a triangular surface mesh provided by the authors of 
Ellis et al. Which is a non-structured mesh of approximately 4 thousand elements. To produce the remaining 
meshes, we use our python script to generate a uniform mesh and round the edges using Trimesh. 
After doing certain refinement studies we noticed that to achieve close results to the original mesh, using a
uniform mesh, we needed to double the density (I HAVE SOME PLOTS ON THIS RESULTS BUT 
I'M NOT SURE IF WE WANT TO PUT THEM, SINCE WE DON'T HAVE SPACE).
To replicate the results of figure S4 on their supplementary material, we use uniform meshes. While for the 
replication of figure 2a and the validation result we used the mesh provided by the authors of Ellis et al.

\textit{dielectric data}
The dielectric data for the simulations, was given by the authors of the paper via a private communication.

To be able to replicate this results, we need to identify the lower frequency mode for each of
the aspect ratios in our computations. For each aspect ratio (AR) 
value from 1 to 7 we computed the extinction cross section $C_{ext}$ across the wave number in the range
800-1000 $cm^{-1}$. We identify the lower frequency mode ($E^{\parallel}_{100}$ in Ellis paper)  that is not a 
longitudinal mode (mode related to the hight of the pillar, only visible when the incidence of the 
electric field is not normal). We can identify the longitudinal modes by comparing normal vs 22 degrees 
angle of incidence runs (see Figure \ref{fig:ellis_ang_inc}). As we mentioned the longitudinal modes, due to its nature, do not appear when we 
have the normal incidence . Then, on the 22 degree incidence computations we choose the lower wave number mode
that it's not a longitudinal mode.

>>>>

 %%% Ellis work summary %%%%
The work of Ellis and coworkers \cite{ellis2016} study the aspect-ratio evolution of high-order
resonant modes in localized surface phonon-polariton nanostructures. They study the
excitation of multipolar localized surface phonon polaritons (SPhP) resonances, by measuring
polarized reflectance on 4H-SiC pillars of fixed height ($H=950$ nm), fixed 
width ($W=400$ nm) and varied length ($L=400-4800$ nm) and therefore an aspect ratio
($AR=L/W=1-12$). These pillars are patterned on a squared grid with a pitch $P=L+500$ nm
to reduce coupling. In  both their simulations and experiments they excite the localized SPhP
resonances, they perform polarized reflectance measurements with the incident polarization 
oriented parallel or perpendicular to the long axis of the pillars.  
 %%% Ellis work summary %%%%

We aim to replicate the computational result presented in Figure S4 of their supplementary 
material (NOT SURE HOW TO CITE THIS) that correspond to the black curve on their plot. In this 
figure they show simulation results for the resonance spectral position of the lower frequency 
mode when having parallel polarization ($E^{\parallel}_{100}$), with an incidence angle of 22$^\circ$.
We first attempted to replicate this result since they have results where the gap between pillars 
is 5000 nm (10 times more than in the experiments and other simulations on the paper), and 
this diminishes the effects of coupling. This result is suitable to compare with 
what we can model using \pygbe.

@@

\textit{methods}
(I DID NOT MENTION ANYTHING RELATED TO WHAT THEY DO IN THE EXPERIMENTS, SHOULD WE INCLUDE THIS?)

In Ellis et al. simulations they solve full Maxwell equations via the RF package of the finite
element method software COMSOL. To represent the array of pillars and their interactions, they use
periodic boundary conditions of one pillar over a portion of substrate, and use periodic boundary conditions on it.
They present the reflectance as a function of the wave number. 
As we mentioned before, we use the boundary element method in 
the quasistatic approximation, which is suitable in these case since Ellis pillar's size is small 
compared to the wavelength involved in the simulations (800-1000 cm$^-1$ which is 10000-12500 nm). We measure 
extinction cross section, which will express as peaks instead of depressions (as seen in Ellis reflection plots)
since you see maximum extinction when there is minimum reflection. The intensity of the peaks is not comparable, but we are 
looking to match the wave number (variable of interest) at which these events happen.

\textit{mesh}
For the case of aspect ratio $AR=4$ we count with a triangular surface mesh provided by the authors of 
Ellis et al. Which is a non-structured (HOW IS IT CALLED WHEN IS FINER WHER THERE ARE CORNERS?) mesh of
approximately four thousand elements. To produce the remaining 
meshes, we use our python script to generate a uniform mesh and round the edges using Trimesh. 
After doing certain refinement studies we noticed that to achieve close results to the original mesh, using a
uniform mesh, we needed approximately double the density (I HAVE SOME PLOTS ON THIS RESULTS BUT 
I'M NOT SURE IF WE WANT TO PUT THEM).
To replicate the results of figure S4 on their supplementary material, we use uniform meshes. While for the 
replication of figure 2a and the validation result we used the mesh provided by the authors of Ellis et al.

\textit{dielectric data}
The dielectric data for the simulations, was given by the authors of the paper via a private communication, 
and corresponds to experimental values of the dielectric.

To be able to replicate the result of Figure S4 of the suplementary material of Ellis et al, we
need to identify the lower frequency mode for each of
the aspect ratios in our computations. For each aspect ratio (AR) 
value from 1 to 7 we computed the extinction cross section $C_{ext}$ across the wave number in the range
800-1000 $cm^{-1}$. We identify the lower frequency mode ($E^{\parallel}_{100}$ in Ellis paper)  that is not a 
longitudinal mode (mode related to the hight of the pillar, only visible when the incidence of the 
electric field is not normal). We can identify the longitudinal modes by comparing normal vs 22 degrees 
angle of incidence runs (see Figure \ref{fig:ellis_ang_inc}). As we mentioned the longitudinal modes, due to its nature, do not appear when we 
have the normal incidence . Then, on the 22 degree incidence computations we choose the lower wave number mode
that it's not a longitudinal mode.
